\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-18 manuscript/main.tex
modified:   analysis/final_analysis.do 	new file:   analysis/individual.do 	modified:   archive/final_analysis.do 	renamed:    cleaning/clean district 8_13.do -> cleaning/clean district.do 	new file:   cleaning/clean individual.do 	new file:   cleaning/merged_back_to_the_individual.ipynb 	modified:   manuscript/main.tex

In the preceding section, our research has been directed toward evaluating the dynamic effect of Lianjia's offline stores operation. However, there is an imperative to conduct a more detailed analysis of the impact of Lianjia's entry on regional transaction properties. The core of this necessary analysis derives from the premise that the entry of a Lianjia represents an exogenous shock within the respective local segmented market, thus providing a unique opportunity to study the effect of offline expansion on local real estate market. To facilitate such an analysis, we have constructed a series of dummy variables associated with the presence of the Lianjia within the marketplace, delineated as $pre_2$, $pre_1$ (before entry), $entry$, $post_1$, $post_2$, and $post_3$ (successive post-entry intervals), which encapsulate the respective temporal epochs relative to the Lianjia's entry. To eliminate the effect of the well constructed effect, we drop all the variables that have Lianjia's offline stores before the year 2016 to better estimate the effect of Lianjia's entry on the market. These binary indicators serve as central regressors within a structured econometric model with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:

>>>>

In the preceding section, our research concentrated on evaluating the dynamic impact of Lianjia's offline store operations. Nevertheless, the presence of a self-selection bias in this dynamic entry factor necessitates the application of causal inference methods to more accurately estimate the effect of Lianjia's offline stores. Consequently, we adopted the Difference-in-Difference (DiD) estimation technique. The foundation of this analysis is predicated on the assumption that the entry of a Lianjia store constitutes an exogenous shock within the local segmented market, thereby providing a unique natural experiment to examine the effects of offline expansion on the local real estate market. Although Lianjia's entry is not a randomized event, the DiD estimation method remains robust in estimating the entry effect by comparing variations in outcome variables before and after Lianjia's entry in the segmented market.

To facilitate such an analysis, we have constructed a series of dummy variables associated with the presence of the Lianjia within the marketplace, delineated as $pre_2$, $pre_1$ (before entry), $entry$, $post_1$, $post_2$, and $post_3$ (successive post-entry intervals), which encapsulate the respective temporal epochs relative to the Lianjia's entry. To eliminate the effect of the well constructed effect, we drop all the variables that have Lianjia's offline stores before the year 2016 to better estimate the effect of Lianjia's entry on the market. These binary indicators serve as central regressors within a structured econometric model with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:
